Structured Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-11-15 R0V0.tex
Finish ADMM paragraph

The alternating direction method of multipliers (ADMM) provides a framework to solve the MI~\eqref{eq:MI formulation} in a distributed fashion \cite{BoydParikhChuEtAl2010,MeissenLessardArcakEtAl2015}. To use this framework, define the sets $\mathbf{S}_{\succ0}^n=\{W\in\mathbb{R}^{n\times n}:W\succ0,W=W^\top\}$, $\mathbf{T}=\{Z\in D^{n\times n}:\exists Y\in\mathbb{R}^{m\times n}, T\prec0\}$. For a set $\mathbf{G}$ define the indicator function $H:\{\mathbf{G}\}\times \mathbb{R}^k\to \{0\}\cup\{\infty\}$ as
\begin{equation*}
	H(\mathbf{G},g)=\begin{cases}
									0,&g\in \mathbf{G}\\
									\infty,&\text{Otherwise.}
								\end{cases}
\end{equation*}

The MI~\eqref{eq:MI formulation} can be cast into the following optimization problem
\begin{equation*}
	\begin{array}{rl}
		\text{minimize}&\displaystyle H(\mathbf{T},Z)+\sum_{i=1}^N H(\mathbf{S}_{\succ0}^{n_i},W_i)\\
		\text{subject to}&\mathbin{\mathtt{diag}}(W_1,\ldots,W_N)-Z=0\;.
	\end{array}
\end{equation*}
The ADMM algorithm can be written as
\begin{equation*}
	\begin{array}{rl}
		W_i^{k+1}:=&\mathbin{\mathtt{argmin}}_{W_i}\left(H(\mathbf{S}_{\succ0}^{n_i},W_i))\right)
	\end{array}
\end{equation*}

>>>>

The alternating direction method of multipliers (ADMM) provides a framework to compute the block-diagonal matrix $W$ to satisfy the MI~\eqref{eq:MI formulation} in a distributed fashion \cite{BoydParikhChuEtAl2010,MeissenLessardArcakEtAl2015}. To use this framework, define the sets $\mathbf{S}_{\succ0}^n=\{W\in\mathbb{R}^{n\times n}:W\succ0,W=W^\top\}$, $\mathbf{T}=\{W_1,\ldots,W_N:\exists Y\in\Xi,(\mathbin{\mathtt{diag}}(W_1,\ldots,W_N),Y)\text{ is a solution to \eqref{eq:MI formulation}}\}$. For a set $\mathbf{G}$ define the indicator function $H:\{\mathbf{G}\}\times \mathbb{R}^k\to \{0\}\cup\{\infty\}$ as
\begin{equation*}
	H(\mathbf{G},g)=\begin{cases}
									0,&g\in \mathbf{G}\\
									\infty,&\text{Otherwise.}
								\end{cases}
\end{equation*}

The MI~\eqref{eq:MI formulation} can be cast into the following optimization problem
\begin{equation*}
	\begin{array}{rl}
		\text{minimize}&\displaystyle H(\mathbf{T},(Z_1,\ldots,Z_N))+\sum_{i=1}^N H(\mathbf{S}_{\succ0}^{n_i},W_i)\\
		\text{subject to}&W_i-Z_i=0,\quad\forall i\in\mathbb{N}_{[1,N]}\;.
	\end{array}
\end{equation*}
The ADMM algorithm can be written as
\begin{enumerate}
	\item For each $i\in\mathbb{N}_{[1,N]}$, update the matrix $W_i$ as follows.
	\begin{equation*}
	\begin{array}{rcl}
		W_i^{k+1}&=&\mathbin{\mathtt{argmin}}_{W_i\in\mathbf{S}_{\succ0}^{n_i}}\left|\left|W_i^k-Z_i^k+\Lambda_i^k\right|\right|_F^2\;,
	\end{array}
\end{equation*}
	where $||\cdot||_F$ stands for the Frobenius norm;

	\item If the matrices $W_1,\ldots,W_N$ belong to $T$, then a solution has been found and the algorithm can be stopped. Otherwise, solve the global problem
	\begin{equation*}
		Z^{k+1}=\mathbin{\mathtt{argmin}}_{Z\in\mathbf{T}}\sum_{i=1}^N\left|\left|W_i^{k+1}-Z_i^k+\Lambda_i^k\right|\right|_F^2\;;
	\end{equation*}
	\item Update $\Lambda$ and return to step 1
	\begin{equation*}
		\Lambda_i^{k+1}=X_i^{k+1}-Z_i^{k+1}+\Lambda_i^k\;.
	\end{equation*}
\end{enumerate}
Note that steps 1 and 3 are computed in parellel while step 2 requires to gather all the values of the matrices $W_i$ and the values $\Lambda_i$.
